---
title       : Iris Key
subtitle    : A classification tree web application
author      : Tavin Cole
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      #
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## A brief survey

* Are you tired of carrying cumbersome printed iris identification keys into the field?
* Are you required to grade my submission for the Developing Data Products course project?
* Do you enjoy working with the [iris data set](http://www.inside-r.org/r-doc/datasets/iris)?

---

## You know, the iris data set

```{r}
str(iris)
```

---

## The answer is ...

If you answered yes to any survey question, please visit my Iris Key application:

https://tavin.shinyapps.io/iris-key/

Please also review the source code:

https://github.com/tavin/iris-key

---

## Thank you and please enjoy some more R code

```{r}
library(caret); library(rpart); library(rpart.plot)
set.seed(226837434)
train(Species ~ ., data = iris, method = 'rpart')$finalModel
```
